Constructing Sailing Match Race Schedules: Round Robin Pairing Lists

### 2015-03-24 paper.tex
Remove some unused packages
Better absolute value formatting

\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{url}
\usepackage{graphics}
\usepackage{graphicx}
\usepackage[all]{xy}
\usepackage{float}
\usepackage{listings}
\usepackage{lipsum}

\usepackage[ruled,vlined]{algorithm2e}
\usepackage{alltt}
\urldef{\mailsa}\path|pat@dcs.gla.ac.uk|
\newcommand{\keywords}[1]{\par\addvspace\baselineskip
\noindent\keywordname\enspace\ignorespaces#1}
\newlength{\halftextwidth}
\setlength{\halftextwidth}{0.47\textwidth}
\usepackage{multicol}
\usepackage{listings}
\usepackage{url}
\usepackage{coffee2}
%\usepackage{amsthm}
%\newtheorem*{definition}{Definition}#
\usepackage{amsopn}

@@

@@

\begin{flalign}
    & \forall_{i\in [0..m-1]} ~ \forall_{j \in [0..f-1]} ~ \sigma.\position[{i,j}] \in \{0,1\} \label{posA} \\
    & \forall_{i \in [0..m-1]} ~ \forall_{j \in [0..f-1]} ~ \sigma.\position[{i,j}] = 1 \iff \sigma.\timeSlot[{m.j+i}] \geq 0 \label{posB} \\
    & \forall_{i \in [0..m-1]} ~ \imbalance[{i}] = |\frac{n-1}{m} - \sum_{j=0}^{f-1} \position[{i,j}]| \label{imbA} \\
& \sigma.\maxImbalance = \sigma.maximum(\sigma.imbalance)  \label{imbB}
\end{flalign}

@@

The final stage, stage 4, orients skippers within matches, such that they are
either port (red) or starboard (green). This is done to satisfy criteria 2 and
3, 5 and 8. A sketch of the constraint model is given with a supporting
diagram, Figure~\ref{oriented}.  A sequence of zero/one constrained integer
variables, of length $n-1$, is produced for each skipper. These correspond to
the sequence of skippers they meet in matches. For example, taking the schedule
in Table~\ref{tab2}, skipper $\sigma[{2}]$ meets skippers in order:
3,0,1,4,5,6, and skipper $\sigma[{5}]$ in the order 4,6,0,1,3,2.  Therefore,
skipper $\sigma[{2}]$'s 4$^{th}$ variable must take a different value from
$\sigma[{5}]$ 5$^{th}$ variable. There are summation constraints on each
skipper to enforce criteria 2 and 3 (equal number of port and starboard
matches). Criteria 8 is enforced by posting constraints such that in a match
($\sigma[{i}],\sigma[{j}]$) where $|i - j| = 1$, the higher indexed skipper
(lower ranked) is on the port side. A DFA constraint is posted for criteria 5
(restricting sequences of port and starboard assignments).

>>>>

\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{url}
\usepackage{graphicx}
\usepackage{float}
\usepackage{listings}
\usepackage[ruled,vlined]{algorithm2e}
\usepackage{mathtools}
\usepackage{coffee2}

@@

\DeclarePairedDelimiter\abs{\lvert}{\rvert}

@@

\begin{flalign}
    & \forall_{i\in [0..m-1]} ~ \forall_{j \in [0..f-1]} ~ \sigma.\position[{i,j}] \in \{0,1\} \label{posA} \\
    & \forall_{i \in [0..m-1]} ~ \forall_{j \in [0..f-1]} ~ \sigma.\position[{i,j}] = 1 \iff \sigma.\timeSlot[{m.j+i}] \geq 0 \label{posB} \\
    & \forall_{i \in [0..m-1]} ~ \imbalance[{i}] = \abs*{\frac{n-1}{m} - \sum_{j=0}^{f-1} \position[{i,j}]} \label{imbA} \\
& \sigma.\maxImbalance = \sigma.maximum(\sigma.imbalance)  \label{imbB}
\end{flalign}

@@

The final stage, stage 4, orients skippers within matches, such that they are
either port (red) or starboard (green). This is done to satisfy criteria 2 and
3, 5 and 8. A sketch of the constraint model is given with a supporting
diagram, Figure~\ref{oriented}.  A sequence of zero/one constrained integer
variables, of length $n-1$, is produced for each skipper. These correspond to
the sequence of skippers they meet in matches. For example, taking the schedule
in Table~\ref{tab2}, skipper $\sigma[{2}]$ meets skippers in order:
3,0,1,4,5,6, and skipper $\sigma[{5}]$ in the order 4,6,0,1,3,2.  Therefore,
skipper $\sigma[{2}]$'s 4$^{th}$ variable must take a different value from
$\sigma[{5}]$ 5$^{th}$ variable. There are summation constraints on each
skipper to enforce criteria 2 and 3 (equal number of port and starboard
matches). Criteria 8 is enforced by posting constraints such that in a match
($\sigma[{i}],\sigma[{j}]$) where $\abs*{i - j} = 1$, the higher indexed skipper
(lower ranked) is on the port side. A DFA constraint is posted for criteria 5
(restricting sequences of port and starboard assignments).
